workshop

### 2023-03-15 scripts/workshop/workshop.Rmd
knit it

vl %<>% mutate(ln_of_mean = log(mean))

@@

ph_range_summ %>% arrange(mean) %>% mutate(name=factor(name, levels=name)) %>% filter(!is.na(species_name)) %>% 
  ggplot(.,aes(y = name, color=ln_of_mean)) +
  geom_linerange(aes(xmin=mean_first,xmax=mean_last,linewidth=1)) + 
  scale_color_viridis_c()
```

>>>>

vl %<>% mutate(ln_of_mean = log1p(mean))

@@

ph_range_summ %<>% rowwise() %>% mutate(median_mo = median(c(mean_first, mean_last)))

ph_range_summ %>% arrange(mean) %>% mutate(name=factor(name, levels=name)) %>% filter(!is.na(species_name)) %>% 
  ggplot(.,aes(y = name, color=ln_of_mean)) + geom_point(aes(x=median_mo, size = 2)) + 
  geom_linerange(aes(xmin=mean_first,xmax=mean_last,linewidth=1)) + 
  scale_color_viridis_c() + guides(size=F, linewidth=F)

ph_range_summ %>% arrange(mean) %>% mutate(abb_name=factor(abb_name, levels=abb_name)) %>% filter(!is.na(species_name)) %>% 
  ggplot(.,aes(y = abb_name, color=ln_of_mean)) + geom_point(aes(x=median_mo, size = 2)) + 
  geom_linerange(aes(xmin=mean_first,xmax=mean_last,linewidth=1)) + 
  scale_color_continuous() + 
  guides(size=F, linewidth=F, color=guide_legend(title="log1p(viral load)")) + 
  theme(axis.text.y = element_text(face = "italic", angle = 15)) + 
  labs(x="Months", y="Species", title = "Average Range of Species Presence")
